Data details

### 2023-02-15 analysis/data-details.qmd
Add details about prior actions

>>>>

## Prior ICCPR actions

To account for whether countries have engaged with ICCPR derogation procedures prior to the COVID-19 pandemic (signalling that they perhaps care about treaty obligations), we include two binary indicators for (1) whether the country has derogated from the ICCPR in the past and (2) whether the country has completed any other type of ICCPR-related actions. These are time-invariant and act more like overall indicator variables, like continent or region.

```{r glimpse-prior-action}
#| code-fold: false
daily_panel %>% 
  group_by(country_name, iso3) %>% 
  summarize(across(starts_with("prior"), ~mean(.))) %>% 
  ungroup() %>% 
  glimpse()
```
